---
title: "DDS Unit05 Homework"
author: "Jeff Leath"
date: "October 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic Setup

Here, I am setting my working directory and loading the packages I need.


```{r}
## set working directory
setwd("C:/Users/jeffl/Dropbox/SMU/MSDS6306_DoingDataScience/Unit05/HW")

## load packages)
library(base)
library("dplyr")

```

## Problem 1: Data Munging

Commentary

```{r }
## bring in file

df <-read.delim('yob2016.txt', header = FALSE, sep = ";", dec = ",")

## name column variables
names(df) <- c("fname", "gender", "count")

## review
head(df)
str(df)

## find name with yyy at the end

prob <-grep("yyy$", df$fname, value = TRUE)
prob

## isolate searched parameter
df_delete <- subset(df, fname=="Fionayyy")
nrow(df_delete)
str(df_delete)

## subset of df to exlcude specific row
y2016 <-df[!grepl("Fionayyy", df$fname),]
str(y2016)


```

## Problem 2: Data Merging

Commentary

```{r }
## read in second file
y2015 <-read.delim('yob2015.txt', header = FALSE, sep = ",", dec = ".")
str(y2015)

## name column variables
names(y2015) <- c("fname", "gender", "count")

## look at the last 10 rows
tail(y2015,10)

## merge tables
final <- merge.data.frame(y2015, y2016, by=c("fname", "gender"))
names(final) <- c("fname", "gender", "2015 Count", "2016 Count")
```
## Problem 3: Data Summary

Commentary

```{r }
## add total column
final$Total <- final$`2015 Count`+final$`2016 Count`
str(final)

# sort by total children (descending)
final2 <- final[order(-final$Total),]
head(final2,10)

# girls only
finalgirls <-subset(final2, gender == 'F')
head(finalgirls,10)

# name and total only
girl2 <- select(finalgirls, fname, Total)
head(girl2,10)

# Write CSV file
write.csv(girl2, file = "TopGirlNames.csv")
```

## Problem 4: GitHub

I have a DDS Homework repo at the link below.

https://github.com/jeffleathMSDS/SMU_MSDS6306

## Codebook

This analysis was a consolidation of two files which listed the number of children named [fname] in birth years 2015 and 2016.

Gender is denoted: M=Male, F=Female

Total: is the sum of named children in both 2015 and 2016

