---
title: "JLEATH_Unit02Live"
author: "Jeff Leath"
date: "September 9, 2018"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown test

This is my file for Unit 02 Homework.

[Jeff Leath](https://www.linkedin.com/in/leath/)

# 1.	 (20 points) Put the following questions into RMarkdown as headers (or subheaders if you’re making question numbers headings). Be sure to answer the questions underneath each header. 

##	a. What is a basic workflow for reproducible research?

-Data Gathering
-Data Analysis
-Results Presentation
 
##	b. What are five practical tips for making research reproducible?

-Document Everything
-Everything is a .txt file
-All files should be human readable
-Explicitly tie your files together
-Have a plan to organize, store, and make your files available


##	c. Give an example of how you might implement each tip.
*-Document Everything* - make a lot of comments in your code

*-Everything is a .txt file* - just requires discipline

*-All files should be human readable* Use proper formating, especially line spacing

*-Explicitly tie your files together* Use good file nameing conventions as well as notations in each file

*-Have a plan to organize, store, and make your files available* Utilize [GetHub](https://github.com)




##	d. Which one of these do you think will be the most difficult?

I think making files human readable will be the hardest part.  The result will depend upon the level of code knowledge the reader has.


# 2.	(20 points) Download and complete “air_hist.R” code from the Files Tab on 2DS.  You will build scatter plots using the plot function.

## a.	As described in the “TODO Assignment 2: Question 2a” comment, complete the plot function regarding monthly temperature.

```{r, include = TRUE}

# This question uses the built-in dataset airquality which has daily air quality 
# measurements in New York from May to September 1973

# Sets the Temperature variable
Temperature <- airquality$Temp

# This is the r code for the scatterplot "Temperature by Month"
plot(x=airquality$Month, y=Temperature, xlab = "Month", ylab = "Temperature", main = "Temperature by Month")
```

## b.	As described in the “TODO Assignment 2: Question 2b” comment, complete the plot function involving ozone.


```{r, include = TRUE}
# This is the r code for the scatterplot "Temperature vs Ozone"
plot(x=Temperature, y=airquality$Ozone, xlab = "Temperature", ylab = "Ozone", main = "Temperature by Ozone")
```


# 3. Download and complete “knit_cars.Rmd” in the Files tab on 2DS. 

## a.	As described in the “TODO Assignment 2: Question 3a” comment, complete a plot function for Temperature and Pressure

```{r, include= TRUE}
## This is the r code to plot Pressure vs Temperature
plot(pressure$pressure, pressure$temperature,  xlab = "Pressure", ylab = "Temperature", main = "Pressure vs Temperature")
```


## b.	As described in the “TODO Assignment 2: Question 3b” comment, complete a similar plot function that reverses the two axes.

```{r, include=TRUE}
## This is the r code to plot Temperature vs Pressure
plot(pressure$temperature, pressure$pressure, xlab = "Temperature", ylab = "Pressure", main = "Temperature vs Pressure")
```




